D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-06-29 doc/article/article.tex
Paper updated

\section{Previous Works}
\cite{arrowrcnn} \\
\cite{interactiveUML} \\
\cite{sketchdiagram}

@@

\subsubsection{Bounding Box Detection}
\label{extr:bbd}
TODO: FasterRCNN - backbone ResNet 50FPN~\cite{rcnn}.  \\ After having determined all the bounding boxes of the diagram image, in order to correctly create the diagram internal representation, there's the need to link together text, elements and relations.\\

@@

\subsection{Object Detection}

TODO: Talk about the net.

The model employed was tested in two different ways: as zero-shot, after a 10-epoch training and after a 100-epoch training. The best-behaving one was, of course, the latter. In Table~\ref{tab:map} and Table~\ref{tab:mar} we show the Mean Average Precision and Recall of the model used.

>>>>

\section{Related Works}
\cite{arrowrcnn} \\
\cite{interactiveUML} \\
\cite{sketchdiagram}

@@

\subsubsection{Bounding Box Detection}
\label{extr:bbd}
The model employed for object detection is a FasterRCNN, relying on a - as backbone - ResNet 50FPN~\cite{rcnn}. The image can be passed rough, and the model automatically resize the image to its own resolution. \\ 
After having determined all the bounding boxes of the diagram image, in order to correctly create the diagram internal representation, there's the need to link together text, elements and relations. For more details about the model and its training, refer to \textbf{Section}~\ref{sec:obj_det}. \\

@@

\subsection{Object Detection}
\label{sec:obj_det}
TODO: Talk about the net.

The model employed was tested in two different ways: as zero-shot, after a 10-epoch training and after a 100-epoch training. The best-behaving one was, of course, the latter (to see the results of the different stages, see \textbf{Figures}~\ref{fig:bbox1} -~\ref{fig:bbox2} -~\ref{fig:bbox3}). In Table~\ref{tab:map} and Table~\ref{tab:mar} we show the Mean Average Precision and Recall of the model used.
\begin{figure}[H]
	\centering
	\includegraphics[width=200pt, height=150pt]{bbox1.jpg}
	\caption{The model employed in a zero-shot fashion.}
	\label{fig:bbox1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=200pt, height=150pt]{bbox2.jpg}
	\caption{The model employed after 10 epochs of training.}
	\label{fig:bbox2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=180pt, height=150pt]{bbox3.png}
	\caption{The model employed after 100 epochs of training. }
	\label{fig:bbox3}
\end{figure}
